The K2 Halo Photometry Campaign

### 2019-03-21 paper/ms.tex
change the output format

% intro kepler
The \kepler Space Telescope was launched with a goal of determining the frequency of Earth-sized planets around Solar-like stars \citep{2010sci...327..977b}, a goal which it has substantially achieved \citep[e.g.][]{2013ApJ...766...81F,2013PNAS..11019273P,2014ApJ...795...64F}. In order to explore these populations it was necessary to observe hundreds of thousands of stars, with the consequence that the \kepler the exposure time and gain were set to optimally observe eleventh or twelfth-magnitude stars, while bright stars are saturated and these saturated stars were intentionally avoided. In the two-wheeled revival as the \ktwo mission, the \kepler telescope observed a sequence of ecliptic-plane fields containing many more very-saturated stars. While it is difficult to obtain precise light curves of these stars because of their saturation, they are some of the most-valuable targets to follow up with photon-hungry methods such as interferometry or high-resolution spectroscopy, and they typically have long histories of previous observations.

@@

The full sample of stars for which halo apertures were obtained is listed in Tables~\ref{table_0}--\ref{table_5}, broken down by Campaign. While some very bright stars were observed with conventional apertures as part of these programs, simple aperture photometry is satisfactory on these targets and we exclude them from the present discussion and data release, which is oriented strictly towards targets only observable with halo photometry. We make an exception for Spica, which was observed in Campaign~6 without a halo aperture but in Campaign~17 with a halo aperture. In Campaign~6 it was assigned a normal aperture by mistake and simple aperture photometry performed extremely poorly, so we have processed it with the halo pipeline.

@@

This work was performed in part under contract with the Jet Propulsion Laboratory (JPL) funded by NASA through the Sagan Fellowship Program executed by the NASA Exoplanet Science Institute. TRW acknowledges the support of the Australian Research Council (grant DP150100250) and the Villum Foundation (research grant 10118). The halo apertures were kindly provided by the K2 team as part of the Guest Observer programs GO6081-7081, GO8025, GO9923, GO10025, GO11047-13047, GO14003-16003, and GO17051-19051, and as a DDT program in Campaign 4 as GO4901. We are grateful for the associated funding provided by the K2 GO office which has been essential in bringing this project to fruition.

>>>>

% intro kepler
The \kepler Space Telescope was launched with a main goal of determining the frequency of Earth-sized planets around Solar-like stars \citep{2010sci...327..977b}, a goal which it has substantially achieved \citep[e.g.][]{2013ApJ...766...81F,2013PNAS..11019273P,2014ApJ...795...64F}. In order to explore these populations it was necessary to observe hundreds of thousands of stars, with the consequence that the \kepler the exposure time and gain were set to optimally observe eleventh or twelfth-magnitude stars, while bright stars are saturated and these saturated stars were intentionally avoided. In the two-wheeled revival as the \ktwo mission, the \kepler telescope observed a sequence of ecliptic-plane fields containing many more very-saturated stars. While it is difficult to obtain precise light curves of these stars because of their saturation, they are some of the most-valuable targets to follow up with photon-hungry methods such as interferometry or high-resolution spectroscopy, and they typically have long histories of previous observations.

@@

The full sample of stars for which halo apertures were obtained is listed in Tables~\ref{table_0}--\ref{table_5}, broken down by Campaign. While some very bright stars were observed with conventional apertures as part of these programs, simple aperture photometry is satisfactory on these targets and we exclude them from the present discussion and data release, which is oriented strictly towards targets only observable with halo photometry. We make an exception for Spica, which was observed in Campaign~6 without a halo aperture but in Campaign~17 with a halo aperture. In Campaign~6 it was assigned a normal aperture by mistake and simple aperture photometry performed extremely poorly, so we have processed it with the halo pipeline. The stars in Campaign~18 were also on-silicon in Campaign~5, but were not assigned apertures suitable for halo photometry in C5. A possible further extension of the present work would be to recover C5 light curves for these objects using either or both of smear or modified halo photometry.

@@

This work was performed in part under contract with the Jet Propulsion Laboratory (JPL) funded by NASA through the Sagan Fellowship Program executed by the NASA Exoplanet Science Institute. TRW acknowledges the support of the Australian Research Council (grant DP150100250) and the Villum Foundation (research grant 10118). The halo apertures were kindly provided by the K2 team as part of the Guest Observer programs GO6081-7081, GO8025, GO9923, GO10025, GO11047-13047, GO14003-16003, and GO17051-19051, and as a Director's Discretionary Time program in Campaign 4 as GO4901. We are grateful for the associated funding provided by the K2 GO office which has been essential in bringing this project to fruition.
